DOpElib:\\ Differential Equations and Optimization Environment

### 2017-07-12 Examples/Documentation/introduction.tex
FAQ for MPI errors in SUSE versions

\subsection*{4.) Different g++ compilers are used for compiling DOpElib and the Examples folder}
\begin{lstlisting}
bernhard@ebook:~/Schreibtisch/Prog/DOpe/Dope/dopelib/Examples> make c-all
cd OPT/StatPDE/Example1; make -s c-all
[ 50%] Building CXX object CMakeFiles/DOpE-OPT-StatPDE-Example1.dir/main.cc.o
c++: error: unrecognized command line option '-fopenmp-simd'
c++: error: unrecognized command line option '-std=c++14'
CMakeFiles/DOpE-OPT-StatPDE-Example1.dir/build.make:62: recipe for target 'CMakeFiles/DOpE-OPT-StatPDE-Example1.dir/main.cc.o' failed
make[4]: *** [CMakeFiles/DOpE-OPT-StatPDE-Example1.dir/main.cc.o] Error 1
CMakeFiles/Makefile2:131: recipe for target 'CMakeFiles/DOpE-OPT-StatPDE-Example1.dir/all' failed
make[3]: *** [CMakeFiles/DOpE-OPT-StatPDE-Example1.dir/all] Error 2
Makefile:83: recipe for target 'all' failed
make[2]: *** [all] Error 2
../../../..//Examples/Make.global_options:2: recipe for target 'c-all' failed
make[1]: *** [c-all] Error 2
Makefile:24: recipe for target 'OPT/StatPDE/Example1' failed
make: *** [OPT/StatPDE/Example1] Error 2
\end{lstlisting}

@@

>>>>

\subsection*{4.) Different g++ compilers are used for compiling DOpElib and the Examples folder}
{\footnotesize
\begin{lstlisting}
bernhard@ebook:~/Schreibtisch/Prog/DOpe/Dope/dopelib/Examples> make c-all
cd OPT/StatPDE/Example1; make -s c-all
[ 50%] Building CXX object CMakeFiles/DOpE-OPT-StatPDE-Example1.dir/main.cc.o
c++: error: unrecognized command line option '-fopenmp-simd'
c++: error: unrecognized command line option '-std=c++14'
CMakeFiles/DOpE-OPT-StatPDE-Example1.dir/build.make:62: 
    recipe for target 'CMakeFiles/DOpE-OPT-StatPDE-Example1.dir/main.cc.o' failed
make[4]: *** [CMakeFiles/DOpE-OPT-StatPDE-Example1.dir/main.cc.o] Error 1
CMakeFiles/Makefile2:131: recipe for target 
    'CMakeFiles/DOpE-OPT-StatPDE-Example1.dir/all' failed
make[3]: *** [CMakeFiles/DOpE-OPT-StatPDE-Example1.dir/all] Error 2
Makefile:83: recipe for target 'all' failed
make[2]: *** [all] Error 2
../../../..//Examples/Make.global_options:2: recipe for target 'c-all' failed
make[1]: *** [c-all] Error 2
Makefile:24: recipe for target 'OPT/StatPDE/Example1' failed
make: *** [OPT/StatPDE/Example1] Error 2
\end{lstlisting}
}

@@

\subsection*{5.) Different g++, cc, cxx compilers are used for compiling
  DOpElib and the Examples folder}

The error message is as before:
{\footnotesize
\begin{lstlisting}
Linking CXX executable ../DOpE-PDE-StatPDE-Example1
/usr/lib64/gcc/x86_64-suse-linux/4.8/../../../../x86_64-suse-linux/bin/ld: cannot find -lmpi_usempi
/usr/lib64/gcc/x86_64-suse-linux/4.8/../../../../x86_64-suse-linux/bin/ld: cannot find -lmpi_mpifh
/usr/lib64/gcc/x86_64-suse-linux/4.8/../../../../x86_64-suse-linux/bin/ld: cannot find -lmpi
collect2: error: ld returned 1 exit status
\end{lstlisting}
}

An alternative to the previous solution is:
\begin{lstlisting}
export DEAL_II_DIR =your_mpi_deal_II_version // only necessary 
      // when not in the standard path
export PATH=/usr/lib64/mpi/gcc/openmpi/bin:${PATH}  // obtain your MPI path
      // with `whereis mpicxx' etc.
export CC=mpicc; export CXX=mpicxx; export FC=mpif90; export FF=mpif77
\end{lstlisting}
Then compile first the DOpElib library and then the Examples folder with these 
settings. Possibly pay attention that also the deal.II version has been
compiled 
with this MPI path.

\begin{remark}
Be careful that you work in the same shell when only using `export'. 
Or include the export lines into the 
\begin{lstlisting}
.bash_rc 
\end{lstlisting}
or 
\begin{lstlisting}
.profile
\end{lstlisting}
file to assert that the correct
compiler is always used.
\end{remark}
